### 2016-09-30 diophantine.tex
Consistent non-usage of commas in symbols()
List the unknown variables for completeness

Currently, the following five types of Diophantine equations can be solved using
SymPy's Diophantine submodule ($a_1, \ldots, a_{n+1}$, $a$, $b$, $c$, $d$, $e$,
$f$, and $k$ are explicitly given rational constants):

@@

>>> x1, x2, x3, x4, x5, x6 = symbols('x1, x2, x3, x4, x5, x6')
>>> diophantine(9*x1**2 + 16*x2**2 + x3**2 + 49*x4**2 + 4*x5**2 - 25*x6**2)
set([(70*t1**2 + 70*t2**2 + 70*t3**2 + 70*t4**2 - 70*t5**2, 105*t1*t5,
420*t2*t5, 60*t3*t5, 210*t4*t5,
42*t1**2 + 42*t2**2 + 42*t3**2 + 42*t4**2 + 42*t5**2)])

>>>>

Currently, the following five types of Diophantine equations can be solved using
SymPy's Diophantine submodule ($a_1, \ldots, a_{n+1}$, $a$, $b$, $c$, $d$, $e$,
$f$, and $k$ are explicitly given rational constants, $x_1, \ldots, x_{n+1}$,
$x$, $y$, and $z$ are unknown variables):

@@

>>> x1, x2, x3, x4, x5, x6 = symbols('x1 x2 x3 x4 x5 x6')
>>> diophantine(9*x1**2 + 16*x2**2 + x3**2 + 49*x4**2 + 4*x5**2 - 25*x6**2)
set([(70*t1**2 + 70*t2**2 + 70*t3**2 + 70*t4**2 - 70*t5**2, 105*t1*t5,
420*t2*t5, 60*t3*t5, 210*t4*t5,
42*t1**2 + 42*t2**2 + 42*t3**2 + 42*t4**2 + 42*t5**2)])
